Crunching Large Graphs with Commodity Processors

### 2011-04-20 doc/hotpar2011/softxmt-hotpar2011.tex
intro one more time

%\documentclass{acm_proc_article-sp}
\documentclass[10pt,nocopyrightspace,preprint]{sigplanconf}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{comment}
\usepackage[labelfont=bf,font=small,belowskip=-3pt,aboveskip=-5pt]{caption}
\usepackage[compact]{titlesec}
\usepackage{mdwlist}
\usepackage{units}

@@

%\textheight 9in
%\textwidth 6.5in
%\columnsep 1pc
\renewcommand{\baselinestretch}{0.8}

@@

@@

The most interesting computational challenge comes from large,
low-diameter, power law graphs: this combination makes extracting
performance difficult. They do not fit in a single commodity machine's
memory. They are difficult lay out with locality, or to partition in a
balanced way~\cite{lang, leskovec}. Expensive inter-node communication
is a limiting factor in scalability~\cite{yoo:parallelbfs}.

@@

%We minimize context size by treating context switches as function
%calls, as in~\cite{charm}. This allows us 
%to save and restore the
%minimum number of registers allowed by the ABI, and 
%Simon:  not really true -- we could save fewer if we knew which of the
%callee save registers weren't going to be clobbered.
\todo{decide whether to change these 2 paragraphs to be inclusive of
  other lightweight implementations, like jump table. I support the
  idea of making it more inclusive but I can't think of what to
  actually change.}  We treat context switches as function calls, as
in~\cite{charm}. This allows us to depend on the compiler to save and
restore caller-save registers while we explicitly save and restore all
the callee-save registers.  We minimize context switch time by doing
all switching and scheduling in user space.

@@

\bibliographystyle{acm}
\bibliography{softxmt-hotpar2011}

\end{document}

>>>>

%\documentclass{acm_proc_article-sp}
\documentclass[10pt,nocopyrightspace]{sigplanconf}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{comment}
\usepackage[labelfont=bf,font=small,belowskip=-3pt,aboveskip=-5pt]{caption}
\usepackage[compact]{titlesec}
\usepackage{mdwlist}
\usepackage{units}

@@

%\textheight 9in
%\textwidth 6.5in
%\columnsep 1pc
\renewcommand{\baselinestretch}{0.8}
%\renewcommand{\baselinestretch}{0}

@@

%\lfoot{USENIX HotPar 2011, Berkeley}

@@

The most interesting computational challenge comes from large,
low-diameter, power law graphs: this combination makes extracting
performance difficult. They do not fit in a single commodity machine's
memory. They are difficult lay out with locality, since every vertex
needs to be near every other vertex. They are difficult to partition
in a balanced way~\cite{lang, leskovec}, leading to hotspots and load
imbalance. High-latency inter-node communication is a limiting factor
in scalability~\cite{yoo:parallelbfs}.

@@

%We minimize context size by treating context switches as function
%calls, as in~\cite{charm}. This allows us 
%to save and restore the
%minimum number of registers allowed by the ABI, and 
%Simon:  not really true -- we could save fewer if we knew which of the
%callee save registers weren't going to be clobbered.
%\todo{decide whether to change these 2 paragraphs to be inclusive of
%  other lightweight implementations, like jump table. I support the
%  idea of making it more inclusive but I can't think of what to
%  actually change.}  
We treat context switches as function calls, as
in~\cite{charm}. This allows us to depend on the compiler to save and
restore caller-save registers while we explicitly save and restore all
the callee-save registers.  We minimize context switch time by doing
all switching and scheduling in user space.

@@

\bibliographystyle{acm}
{\small
\bibliography{softxmt-hotpar2011}
}
\end{document}
